Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-04-07 05_Presentation/MPSA_AID_Paper_Presentation.tex

\begin{itemize}
    \item China seems to deliberately keep its foreign aids secret
    \item However, aids as part of the "South-South cooperation" improve China's image abroad.
    \item Two opposite modes of interactions: foreign aids and media/public diplomacy -- secret and open
\end{itemize}

@@

\begin{itemize}
    \item Research Question: How does China’s foreign aid relate to Beijing’s efforts at public diplomacy and international recognition?

   \item Argument: Countries that receive higher media exposure and diplomacy efforts are
strategically more important to Beijing, and in turn receive disproportionally larger China’s
foreign aid.

\end{itemize}
\end{frame}

@@

\begin{itemize}
    \item state-sponsored \textit{Xinhua} mediac coverage of developing countries intended for foreign audiences
    \item China’s bilateral South-South diplomatic activities

@@

Developing countries that receive \textbf{higher} media coverage and diplomatic visit are strategically more important than the others. Hence, they get \textbf{more} benefits of aids.

@@

Similar to Western donors, the transparency of foreign aid arguably serve China’s interests.
\end{frame}

\begin{frame}{Motivations behind Chinese Foreign Aid}
The obscurity seems to have more to do with capacity and logistics, rather than intention \begin{footnotesize} (Dreher et al. 2018) \end{footnotesize}. We
explore the \textbf{connections }between China’s bilateral development finance and other, visible,
activities linked to diplomatic and legitimacy-seeking objectives.

@@

\begin{itemize}
\item What's covered in the news signal to the public what is important \begin{footnotesize} (McCombs \& Shaw, 1972) \end{footnotesize}

@@

\item Xinhua has dual roles: reporting news and building the China
image as part of Beijing’s “going out” strategy \begin{footnotesize} (Shambaugh, 2015) \end{footnotesize}

@@

\item Diplomatic visit is a signal of support and proximity of
the countries.

@@

\item We expect China to prioritize giving foreign
aid to its “friends” -- countries where China has developed strong relationships through
public diplomacy efforts.

@@

\begin{itemize} 
    \item \textit{H1:} When developing countries receive more media exposure in Xinhua, they are more
likely to receive more foreign aid from China.
    \item \textit{H2:} When developing countries host or visit Chinese high-level diplomatic visits more
frequently, they are more likely to receive more foreign aid from China.
\end{itemize}

@@

Unique recipient-year observations from 2000 to 2014

@@

\item IV: counts of country media coverage (Millions of English edition Xinhua news articles scraped by the Cline Center for Advanced Social Research)

@@

\item Covariates: aid recipient characteristics (GDP, presence of war, disasters, political and civil liberties) and bilateral characteristics between China and aid recipients (economic ties, alliances)

\item Model Specifications: OLS with robust standard errors clustered by recipients; Tobit maximum likelihood estimator; selection and level equations; instrumental variables

@@

@@

>>>>

\begin{itemize}
    \item China seems to deliberately keep its foreign aid giving a secret.
    \item However, development finace arguably should promote "South-South cooperation" and improve China's image abroad.
    \item \textit{Such goals require transparency, so what should we make of its absence?}
\end{itemize}

@@

\begin{itemize}
\item \textbf{The Puzzle}: \textit{Absent formal modes of transparency, what evidence do we have that Chinese aid serves public diplomacy?}
\item \textbf{Argument}: \textit{We should observe complementarties between where China sends a greater number of diplomatic missions and that receive greater media coverage in outlets targeted at foreign audiences with where China gives greater foreign aid.}
\end{itemize}

@@

\begin{itemize}
    \item State-sponsored \textit{Xinhua} mediac coverage of developing countries intended for foreign audiences
    \item China’s bilateral South-South diplomatic activities

@@

Developing countries that receive \textbf{higher} media coverage and diplomatic visit are strategically more important than the others. Hence, they get \textbf{more} aid.

@@

Like Western donors, China should have an interest in generating goodwill toward Beijing.

\begin{itemize}
    \item US cites benefits from public branding of tsunami relief to Indonesia in 2004.
    \item Surveys of policymakers show increasing influence of Beijing.
\end{itemize}

The obscurity seems to have more to do with capacity and logistics, rather than intention \begin{footnotesize} (Dreher et al. 2018) \end{footnotesize}. We
explore the \textbf{connections }between China’s bilateral development finance and other, visible,
activities linked to diplomatic and legitimacy-seeking objectives.

@@

\begin{itemize}
\item What's covered in the news signals to the public what is important \begin{footnotesize} (McCombs \& Shaw, 1972) \end{footnotesize}

@@

\item \textit{Xinhua} has dual roles: reporting news and building the China
image as part of Beijing’s “going out” strategy \begin{footnotesize} (Shambaugh, 2015) \end{footnotesize}

@@

\item Diplomatic visit is a signal of support and closeness of countries.

@@

\item We expect China to prioritize giving foreign
aid to its “friends” -- countries where China has developed strong relationships through
public diplomacy efforts -- and to countries it seeks to highlight to Western audiences.

@@

\begin{itemize} 
    \item \textit{H1:} When developing countries receive more media exposure in \textit{Xinhua}, they are more
likely to receive more foreign aid from China.
    \item \textit{H2:} When developing countries host Chinese high-level diplomatic visits more
frequently, they are more likely to receive more foreign aid from China.
\end{itemize}

@@

Unique recipient-year observations from 2001 to 2014

@@

\item IV: counts of country media coverage (Millions of English edition \textit{Xinhua} news articles scraped by the Cline Center for Advanced Social Research)

@@

\item Covariates: aid recipient characteristics (GDP, presence of civil war, disasters, political and civil liberties) and bilateral characteristics between China and aid recipients (economic ties, alliances)

\item Model Specifications: $\text{ihs(aid}_{rt}) = \tau_t + \beta_1\text{ihs(coverage}_{rt}) + \beta_2\text{ihs(visits}_{rt}) + X_{rt}^\top \gamma + \epsilon_{rt}.$

\item Estimation: OLS (CR1 errors), Tobit (random recipient intercepts), Logit/Selection (random recipient intercepts), Level/OLS (CR1 errors), Lagged IV (CR1 errors), Lewbel IV (CR1 errors).

@@

\begin{table}

\caption{Model Estimates}
\centering
\begin{tabular}[t]{lr>{}lr>{}lr>{}lr>{}lr>{}lr>{}l}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Linear} & \multicolumn{2}{c}{Tobit} & \multicolumn{2}{c}{Selection} & \multicolumn{2}{c}{Level} & \multicolumn{2}{c}{IV Lag} & \multicolumn{2}{c}{IV Lewbel} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11} \cmidrule(l{3pt}r{3pt}){12-13}
  & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI\\
\midrule
Coverage & 0.63 & \includegraphics[width=0.67in, height=0.17in]{} & 1.29 & \includegraphics[width=0.67in, height=0.17in]{} & 0.18 & \includegraphics[width=0.67in, height=0.17in]{} & 0.11 & \includegraphics[width=0.67in, height=0.17in]{} & 0.67 & \includegraphics[width=0.67in, height=0.17in]{} & 0.51 & \includegraphics[width=0.67in, height=0.17in]{}\\
Visits & 0.93 & \includegraphics[width=0.67in, height=0.17in]{} & 1.54 & \includegraphics[width=0.67in, height=0.17in]{} & 0.21 & \includegraphics[width=0.67in, height=0.17in]{} & 0.36 & \includegraphics[width=0.67in, height=0.17in]{} & 1.08 & \includegraphics[width=0.67in, height=0.17in]{} & 1.38 & \includegraphics[width=0.67in, height=0.17in]{}\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{frame}{Conclusion}

\begin{itemize}
    \item Despite a lack of formal transparency China's foreign aid serves a public role.
    \item Beijing's development finance complements its efforts at south-south diplomacy.
    \item And its development finance complements media coverage of aid recipients targted at Western audiences.
\end{itemize}

\textbf{Like Western donors, visibility foreign aid serves China’s interests.}
\end{frame}
